ggalluvial: Layered Grammar for Alluvial Plots

### 2020-03-25 paper/paper.rmd

<!--
To generate `paper.md`, execute this from the console:
```r
knitr::knit("paper/paper.rmd", "paper/paper.md")
```
-->

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "paper/"
)
```

>>>>

<!--
To generate `paper.md`, execute this from the console:
```r
knitr::knit("paper.rmd", "paper.md")
```
-->

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = ""
)
```
